---
title: "EIKIFJB"
output: html_notebook
---

This script creates a hex sticker with the abbreviation "EIKIFJB" (Everything I know is from Jenny Bryan)


```{r setup}

library(hexSticker)
library(showtext)

library(here)

```


Fonts from [Google fonts](http://www.google.com/fonts)


The image credit:

Source: https://www.flaticon.com/free-icon/laptop_22787?term=laptop%20fire&page=1&position=1

<div>Icon made by <a href="https://www.flaticon.com/authors/freepik" title="Freepik">Freepik</a> from <a href="https://www.flaticon.com/" title="Flaticon">www.flaticon.com</a></div>

The image is licensed by Flaticon as "Free for personal and commercial purpose with attribution."


### Sigmar One

```{r}

## Loading Google fonts (http://www.google.com/fonts)
font_add_google("Sigmar One", "sigmar")
## Automatically use showtext to render text for future devices
showtext_auto()

## 
sticker(here("img", "fire_256.png"), package="EIKIFJB",  
        s_x=1, s_y=0.85, s_width=0.5, s_height=0.5,
        h_fill = "white", h_color = "#16161D",
        p_size=24, p_color = "#B22222",
        p_y = 1.45,
        p_family = "sigmar", 
        url = "'Everything I know is from Jenny Bryan' @sharlagelfand",
#        u_angle = 151,
        u_color = "#B22222",
        u_size = 3,
        filename="EIKIFJB_sigmar_hex.png")

```




## An alternate image, and playing about with some different fonts

Laptop image by andreas160578 from Pixabay; free for commercial use, no attribution required

https://pixabay.com/photos/laptop-burning-fire-stress-support-1895382/



### Sigmar One

```{r}

## Loading Google fonts (http://www.google.com/fonts)
font_add_google("Sigmar One", "sigmar")
## Automatically use showtext to render text for future devices
showtext_auto()

## 
sticker(here("img", "lappy.jpg"), package="EIKIFJB",  
        s_x=1, s_y=0.85, s_width=1.0, s_height=1.0,
        h_fill = "white", h_color = "#16161D",
        p_size=24, p_color = "#B22222",
        p_y = 1.45,
        p_family = "sigmar", 
        url = "'Everything I know is from Jenny Bryan' @sharlagelfand",
        u_angle = 151,
        u_color = "#B22222",
        u_size = 3,
        filename="EIKIFJB_sigmar_hex_photo.png")

```




### Russo One

```{r}

## Loading Google fonts (http://www.google.com/fonts)
font_add_google("Russo One", "russo")
## Automatically use showtext to render text for future devices
showtext_auto()

## 
sticker(here("img", "lappy.jpg"), package="EIKIFJB",  
        s_x=1, s_y=0.8, s_width=1.0, s_height=1.0,
        h_fill = "white", h_color = "#16161D",
        p_size=26, p_color = "#E24C00",
        p_y = 1.45,
        p_family = "russo", 
        filename="EIKIFJB_russo_hex.png")

```




### Anton

```{r}

## Loading Google fonts (http://www.google.com/fonts)
font_add_google("Anton", "anton")
## Automatically use showtext to render text for future devices
showtext_auto()

## 
sticker(here("img", "lappy.jpg"), package="EIKIFJB",  
        s_x=1, s_y=0.8, s_width=1.0, s_height=1.0,
        h_fill = "white", h_color = "#16161D",
        p_size=30, p_color = "#4B0082",
        p_y = 1.45,
        p_family = "anton", 
        filename="EIKIFJB_anton_hex.png")

```



## Dishwasher variant

https://twitter.com/JennyBryan/status/1248280289446481920?s=20

Icons made by <a href="https://www.flaticon.com/authors/freepik" title="Freepik">Freepik</a> from <a href="https://www.flaticon.com/" title="Flaticon"> www.flaticon.com</a>



```{r}

## Loading Google fonts (http://www.google.com/fonts)
font_add_google("Sigmar One", "sigmar")
## Automatically use showtext to render text for future devices
showtext_auto()

## 
sticker(here("img", "dishwasher_blue.png"), package="EIKIFJB",  
        s_x=1, s_y=0.80, s_width=0.45, s_height=0.45,
        h_fill = "white", h_color = "#16161D",
        p_size=24, p_color = "#4677D4",
        p_y = 1.45,
        p_family = "sigmar", 
        url = "'Everything I know is from Jenny Bryan' @sharlagelfand",
#        u_angle = 151,
        u_color = "#B22222",
        u_size = 3,
        filename="EIKIFJB_sigmar_hex.png")

```


